\section{Conclusion}\label{sec:Conclusion}

% Summary
% Adaptation depends on previous patterns
We observed that during natural image stimulation, many ganglion cells change
their selectivity for different parts of the images depending on previous light
patterns.

% Modeling and Simulation
We combined large-scale recordings of RGC responses to natural movie
stimulations with CNN-based modeling to investigate such mechanisms of fast
contrast adaptation in the retina.
% Well I don't really have the rest to say here since it's not done

% Interplay of different subunit pathways
Under realistic regularization constraints, the CNNs learned a structure
similar to retinal pathways, where a ganglion cell activation is the result of
a pooling of local subunits of different types in a specific area in space, the
ganglion cell receptive field.

% Neural cells encode spatio-temporal features of natural scenes
Our result supports the idea that retinal ganglion cells encode both
spatial and temporal features of natural scenes on a local scale.
Previous works have described those features to be encoded as features of the
retinal response (latency, firing rate). We might be able to support this
theory with further comparison of measured responses with predicted responses
of
our model.

% Future Directions

Our work in the following months should take multiple directions. First, we are
investigating how more complex models perform on the prediction of LSTA (see
Annexe 1).
Second, we want to study if adding divisive non-linear temporal
dynamic in the subunits could help take the effect of the adaptation images
into
account (see Annexe 2).
Third, we would be interested to see if the LSTA adaptation is only dependent
on the local luminance of the adaptatio images or also on the local temporal
contrast. To do that we could add flickering of different speed to the black
and white checks.

% Comparative analysis

% Utility of measurements tools
Maheswaranathan and colleagues \citep{maheswaranathan_interpreting_2023} have
recently
been able to predict different aspect of encoding in the retina using deep
comvolutional network. In comparison, our experimental approach of estimating
the LSTA allow a direct comparison from the model to the data. Classical
estimation of performance can't describe what is missed in the prediction,
while our qualitative comparison might be able to.

% The what, why and how the retina
% I think it's and accessible illustration of the main questions regarding the retinal code
The modeling of retinal responses to natural stimuli has improved our
understanding of complex retinal processing. In a recent review, Karamanlis and
colleagues \citep{} [ADD TO BIB], suggested three perspectives of study on the
retinal
encoding of natural scenes: The circuit perspective ('How is the retinal code
implemented?'), the normative perspective ('Why is it complimented this way?)
and the coding perspective ('What is the code used by the retina?'). In this
work, we focused on the 'what' for now. By exploring the response of the retina
to a portion of
the spatio-temporal stimuli space we can gain insight into the code used by the
retina on that subspace. To explore further the 'how' perspective, one would
need to study how the different known types of cells in the retina participate
in that encoding. This poses the challenge of bridging the typing of cells from
functional and anatomical perspectives.
The normative perspective has also been explored using deep CNNs with
anatomically realistic constrained. It is likely that species with simpler
cortical circuitry, as mice, have a stronger need for upstream feature
extraction, in the retina [ADD CITE]. In opposition, species with computationally powerful
cortexes such as primates can deal with more faithful and linear
representations
of the visual inputs.